%************************************************
\chapter{Curriculum Vitae}
\label{chp:Curriculum Vitae}
%************************************************
Prior to my time at BCIT, my computer programming skills were entirely self-taught. As such, it has been my objective at BCIT to formalize and hone my skills with respect to computer programming as well as expanding my knowledge into other sub-disciplines, such as data communications and network security.

Ultimately, upon graduation, my goal is to seek employment in the field of *NIX/BSD systems programming with a focus on data communications. With this goal in mind, I have constructed an experimental practicum with a focus on the skills that I have learnt during my tenure at BCIT.

\clearpage
\section{Formal Education}
My formal education has been somewhat fragmented as I have had several false starts over the past 20 years. Due to personal issues, I ended up dropping out of high school in 1994, which I ultimately finished at night school in 2002.

After a brief stint at UBC with an eye on physics, I decided to enrol at BCIT with the intention of completing the Bachelor of Technology program. \\

\noindent
\begin{tabular}{l l}
\textbf{2007 - 2012} & \textbf{British Columbia Institute of Technology} \\
& Bachelor of Technology Program - Dual Option: \\
& \emph{- Network Security \& Administration} \\
& \emph{- Data Communications \& Internetworking} \\
& \\
\textbf{2003-2004} & \textbf{University of British Columbia} \\
& Bachelor of Science 1\textsuperscript{st} Year - Physics \\
& \\
\textbf{2001-2002} & \textbf{Main Street Education Centre} \\
& Completed Grade 12 \\
& \\
\textbf{2001-2002} & \textbf{Lucas Centre} \\
& Completed Grades 10 \& 11 \\
& \\
\textbf{1992-1994} & \textbf{Semiahmoo Secondary School} \\
& Completed Grades 8 \& 9 \\
\end{tabular}

\clearpage
\section{Work Experience}
The majority of my work experience has been with Highlight Investments, as I helped found the company and remained with there for 13 years. During my time with Highlight Investments I was afforded the opportunity to learn how to program perform systems and network administration. This included the administration of our co-located web, firewall, email, and database servers.

With the launch of our main stock index volume analysis tools, new development ceased and the company moved into maintenance mode. Given the lack of new and interesting projects to work on, I decided to go back to school in order to further my career. \\

\noindent
\begin{tabular}{l l}
\textbf{1997-2010} & \textbf{Highlight Investments Research Group} \\
& \emph{Systems Support \& Operations - Stock Index Volume Analysis} \\
& - Pivotal role in creating \& incorporating the company \\
& - Designed prototype stock market analysis tools \\
& - Patented a stock volume normalization technique \\
& - Published in \emph{The Technical Analyst} magazine \\
& - Linux \& Windows systems \& network administration \\
& - Retained for consulting \\
& \\
\textbf{1996-1997} & \textbf{Kona Norgren Enterprises} \\
& \emph{Owner/Operator - Floral Delivery} \\
& - Accounting, taxes, \& payroll \\
& - Delivery \& courier dispatch \\
& - Day-to-day management \& administration \\
& \\
\textbf{1992-1996} & \textbf{Nectar Concepts Inc.} \\
& \emph{Computer Consultant - Snowboard Manufacturer} \\
& - Created CAD/CAM drafting solution for manufacturing \\
& - Created \& maintained office coaxial network \\
& - Systems administration \& maintenance \\
\end{tabular}

\clearpage
\section{Areas of Specialization}
The majority of my work over the past decade has focused on some area of network security and data communications (e.g. the delivery of real-time stock market data and securing database servers from SQL injection attacks). What I gamed throughout my career is a better understanding of what I find truly fascinating with respect to my field: low-level systems programming.

I am currently nearing the end of my Bachelor of Technology degree at BCIT; with a dual option in Network Security and Data Communications. It is with these specializations and my interest in low-level systems programming in mind that I have designed a practicum that draws from each area of expertise in other to more fully make use of what I have learnt during my time with the program.